High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-22 notebooks/mnist.qmd
seem to finally be getting somewhere

```{julia}
cov = .95
conf_model = conformal_model(jem; method=:adaptive_inductive, coverage=cov)
mach = machine(conf_model, X, labels)
fit!(mach)
M = ECCCo.ConformalModel(mach.model, mach.fitresult)
```

@@

@@

η=0.1

# ECCCo:
λ=[0.0,0.0,10.0]
temp=0.5

# Generate counterfactual using ECCCo generator:
generator = ECCCoGenerator(
    λ=λ, 
    temp=temp, 
    opt=Flux.Optimise.Adam(),
)
ce_conformal = generate_counterfactual(
    x, target, counterfactual_data, M, generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)

>>>>

```{julia}
cov = .95
conf_model = conformal_model(jem; method=:simple_inductive, coverage=cov)
mach = machine(conf_model, X, labels)
fit!(mach)
M = ECCCo.ConformalModel(mach.model, mach.fitresult)
```

@@

```{julia}
𝒟x = Uniform(-1,1)
𝒟y = Categorical(ones(K) ./ K)
sampler = UnconditionalSampler(𝒟x; input_size=(D,))
conditional_sampler = ConditionalSampler(𝒟x, 𝒟y; input_size=(D,))
opt = ImproperSGLD()
n_iter = 100
```

η=1.0

# Generate counterfactual using generic generator:
generator = GenericGenerator()
ce_wachter = generate_counterfactual(
    x, target, counterfactual_data, M, generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
)

# ECCCo:
λ=[0.0,1.0,10.0]
temp=0.01

# Generate counterfactual using ECCCo generator:
generator = ECCCoGenerator(
    λ=λ, 
    temp=temp, 
)
ce_conformal = generate_counterfactual(
    x, target, counterfactual_data, M, generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)

@@
